Community Detection in the Setting of Generalized Random Dot Product Graphs

### 2023-01-10 slides/slides.Rmd
fixed a couple typos
fixed a typo
script ells

* $P_{ij} = \theta_{z_i z_j}$
* $K (K + 1) / 2$ parameters $\theta_{kl}$

@@

* $P_{ij} = \theta_{z_i z_j} \omega_i \omega_j$
* $K (K + 1) / 2 + n$ parameters $\theta_{kl}$, $\omega_i$

@@

SBM $\to$ Erdos-Renyi: $\theta_{kl} = \theta$

@@

$$\ell(z, \theta; A) = \sum_{i<j} \sum_{k, \ell} z_{ij} z_{j \ell} \Big(A_{ij} \log_{k \ell} + (1 - A_{ij}) \log(1 - \theta_{k \ell}) \Big)$$

@@

1. Let each $P^{(kl)}$ denote the $n_k \times n_l$ matrix of edge probabilities 
between communities $k$ and $l$. 
2. Organize popularity parameters as vectors 
$\lambda^{(kl)} \in \mathbb{R}^{n_k}$ 
such that $\lambda^{(kl)}_i = \lambda_{k_i l}$ is the popularity parameter 
of the $i$^th^ vertex of community $k$ towards community $l$. 
3. Each block can be decomposed as 
$P^{(kl)} = \lambda^{(kl)} (\lambda^{(lk)})^\top$.

@@

$$A \sim \PABM(\{\lambda^{(kl)}\}_K) \iff A \sim \GRDPG_{p, q}(X U)$$

@@

**Corollary**: The ASE of $A \sim \PABM(\{\lambda^{(kl)}\}_K)$ lies near a collection of $K$-dimensional subspaces in $K^2$ dimensions.

@@

Noroozi et al. observed that the rank of $P$ is $K^2$ 
and the columns of $P$ belonging to each community has rank $K$ 
to justify SSC for the PABM.

>>>>

* $P_{ij} = \theta_{z_i z_j}$
* $K (K + 1) / 2$ parameters $\theta_{k \ell}$

@@

* $P_{ij} = \theta_{z_i z_j} \omega_i \omega_j$
* $K (K + 1) / 2 + n$ parameters $\theta_{k \ell}$, $\omega_i$

@@

SBM $\to$ Erdos-Renyi: $\theta_{k \ell} = \theta$

@@

$$\ell(z, \theta; A) = \sum_{i<j} \sum_{k, \ell} z_{ik} z_{j \ell} \Big(A_{ij} \log_{k \ell} + (1 - A_{ij}) \log(1 - \theta_{k \ell}) \Big)$$

@@

1. Let each $P^{(k \ell)}$ denote the $n_k \times n_l$ matrix of edge probabilities 
between communities $k$ and $l$. 
2. Organize popularity parameters as vectors 
$\lambda^{(k \ell)} \in \mathbb{R}^{n_k}$ 
such that $\lambda^{(k \ell)}_i = \lambda_{k_i l}$ is the popularity parameter 
of the $i$^th^ vertex of community $k$ towards community $l$. 
3. Each block can be decomposed as 
$P^{(k \ell)} = \lambda^{(k \ell)} (\lambda^{(lk)})^\top$.

@@

$$A \sim \PABM(\{\lambda^{(k \ell)}\}_K) \iff A \sim \GRDPG_{p, q}(X U)$$

@@

**Corollary**: The ASE of $A \sim \PABM(\{\lambda^{(k \ell)}\}_K)$ lies near a collection of $K$-dimensional subspaces in $K^2$ dimensions.

@@

Noroozi et al. observed that the rank of $P$ is $K^2$ 
and the columns of $P$ belonging to each community have rank $K$ 
to justify SSC for the PABM.
